---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rnotify

A very simple wrapper around `node-notifier CLI`, "A Node.js module for sending notifications on native Mac, Windows and Linux (or Growl as fallback)" [link](https://github.com/mikaelbr/node-notifier).

## Installation

### Node Module

__You'll need to have a working installation of the Node JS module `node-notifier-cli`__, which you can install with:

```
sudo npm i -g node-notifier-cli
```

Check that it works by running in your console: 

```
notify -t "Hello" -m "My Message"
```

### R Package

```{r eval = FALSE}
remotes::install_github("ColinFay/rnotify")
```

## Run

Launch notification with:

```{r eval = FALSE}
library(rnotify)
new_notif(
  title = "Computation finished", 
  message = "Go back to R!"
)
```

Only title and message are mandatory. Other possible args are: 

+ `subtitle` Subtitle of the notification (not available on windows).
+ `icon` Icon of the notification
+ `sound` Sound of the notification
+ `time` Time in milliseconds of the notification.


## Returned object

The returned object from `new_notif()` is the result `processx::process$new()` and can be handled as such. 

## CoC

Please note that the `rnotify` project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
